An indexed construction of semi-simplicial and semi-cubical types

### 2022-05-18 paper/paper.tex
paper: proof-of-concept xkeyval on tab-frames

% Frame, layer, and filler: the general macro
\makeatletter
\newcommandx{\prim}[6][2=,3=,4=,5=,6=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}\@ifstar{}{\setkeys*{Ex}{#6}}}}
\makeatother

% Restriction for frame, layer, and filler: the general macro
\makeatletter
\newcommandx{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}\@ifstar{}{\setkeys*{Ex}{#8}}}}
\makeatother

@@

% Hack: we'd like \coh to take 10 arguments, with the 10th being passed to
% xkeyval, but this is not possible. The only possible compromise is to join
% #7, and #8 by hand in usage of \coh, by hand.
\makeatletter
\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}\@ifstar{}{\setkeys*{Ex}{#9}}}}
\makeatother

% Some abbreviations
\newcommand{\imp}{\ensuremath{\rightarrow}}
\newcommand{\overright}[1]{\ensuremath{\overrightarrow{#1}}}
\renewcommand{\D}{\ensuremath{(D)}}
\newcommand{\hdD}{\ensuremath{(D.1)}}
\newcommand{\tlD}{\ensuremath{(D.2)}}
\renewcommand{\d}{\ensuremath{(d)}}
\newcommand{\E}{\ensuremath{(E)}}
\renewcommand{\l}{\ensuremath{(l)}}
\renewcommand{\c}{\ensuremath{(c)}}

>>>>

% Frame, layer, and filler: the general macro
\makeatletter
\newcommandx{\prim}[6][2=,3=,4=,5=,6=]{\ensuremath{\mathsf{\color{indian-yellow}{#1}}_{#2}^{\joinargs{}[#3][#4][#5]}}\@ifstar{}{\setkeys*{Ex}{#6}}}
\makeatother

% Restriction for frame, layer, and filler: the general macro
\makeatletter
\newcommandx{\restr}[8][2=,3=,4=,5=,6=,7=,8=]{\ensuremath{\mathsf{\color{russian-green}{restr}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4]}^{\joinargs{}[#5][#6][#7]}}\@ifstar{}{\setkeys*{Ex}{#8}}}
\makeatother

@@

% Hack: we'd like \coh to take 10 arguments, with the 10th being passed to
% xkeyval, but this is not possible. The only possible compromise is to join
% #7, and #8 by hand in usage of \coh, by hand.
\makeatletter
\newcommandx{\coh}[9][2=,3=,4=,5=,6=,7=,8=,9=]{\ensuremath{\mathsf{\color{chestnut}{coh}}_{\mathsf{\color{indian-yellow}{#1}}\joinargs{,}[#2][#3][#4][#5][#6]}^{\joinargs{}[#7][#8]}}\@ifstar{}{\setkeys*{Ex}{#9}}}
\makeatother

% Some abbreviations
\newcommand{\imp}{\ensuremath{\rightarrow}}
\newcommand{\overright}[1]{\ensuremath{\overrightarrow{#1}}}
\renewcommand{\D}{\ensuremath{(D)}}
\newcommand{\hdD}{\ensuremath{(D.1)}}
\newcommand{\tlD}{\ensuremath{(D.2)}}
\renewcommand{\d}{\ensuremath{(d)}}
\newcommand{\E}{\ensuremath{(E)}}
\renewcommand{\l}{\ensuremath{(l)}}
\renewcommand{\c}{\ensuremath{(c)}}
\newcommand{\pair}[2]{\ensuremath{(#1, #2)}}
